---
title: "For Loops in R"
author: "Audrey Olson"
date: "5/25/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

These are taken directly from https://www.r-exercises.com/2018/03/30/loops-in-r-exercises/

Exercise 1

Write a for loop that iterates over the numbers 1 to 7 and prints the cube of each number using print().

```{r}

```


Exercise 2

Write a for loop that iterates over the column names of the inbuilt iris dataset and print each together with the number of characters in the column name in parenthesis. Example output: Sepal.Length (12). Use the following functions print(), paste0() and nchar().

```{r}

```


Exercise 3

Write a while loop that prints out standard random normal numbers (use rnorm()) but stops (breaks) if you get a number bigger than 1.

```{r}

```


Exercise 4

Using next adapt the loop from last exercise so that doesn’t print negative numbers.

```{r}

```


Exercise 5

Using a for loop simulate the flip a coin twenty times, keeping track of the individual outcomes (1 = heads, 0 = tails) in a vector that you preallocte.

```{r}

```


Exercise 6

Use a nested for loop (a for loop inside a for loop) that produces the following matrix, preallocate the matrix with NA values.

    0     1     2     3     4
    1     0     1     2     3
    2     1     0     1     2
    3     2     1     0     1
    4     3     2     1     0
    
```{r}

```


Exercise 7

Use a while loop to investigate the number of terms required before the product

1⋅2⋅3⋅4⋅…

reaches above 10 million.

```{r}

```


Exercise 8

Use a while loop to simulate one stock price path starting at 100 and random normally distributed percentage jumps with mean 0 and standard deviation of 0.01 each period. How long does it take to reach above 150 or below 50?

```{r}

```


Exercise 9

Implement a simple version of Guess the number game using a while loop. The user should guess a number between 1 and 10, you can use scan() to get user input. The loop should break if the user guesses 5.

```{r}

```


Exercise 10

Implement a multiplication game. A while loop that gives the user two random numbers from 2 to 12 and asks the user to multiply them. Only exit the loop after five correct answers. Try using as.integer(readline()) instead of scan() this time.

```{r}



```

