---
title: "Recursive Function Exercise"
author: "Audrey Olson"
date: "5/25/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

For all of these functions, you will learn the most if you:

  a. First try your hardest to do it without looking anything up. SERIOUSLY.
  b. Then, allow yourself to Google function terms and other shortcuts. 
  c. THEN, when you've exhausted all of your own efforts, permit yourself to look at examples. 
  d. THEN, compare examples for common elements/structures. Summarize what's in commong.
  e. FINALLY, try again, by yourself, to see how far you can get on your own.
  f. Repeat d. and e. until you are able to author a recursive function of your own for these problems. Oh, wait, I just trapped you in a recursive Rmarkdown script writing function! Muhahahaha!

Hint: use Recall within the function to make reference to the function itself, just as you would use the function name with ().

~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

Write a recursive function that calculates the Fibonacci sequence.

Via Wikipedia: https://en.wikipedia.org/wiki/Fibonacci_number 
"In mathematics, the Fibonacci numbers, commonly denoted Fn, form a sequence, called the Fibonacci sequence, such that each number is the sum of the two preceding ones, starting from 0 and 1. ... The sequence unfolds as follows: 0, 1, 1, 2, 3, 5, 8, 13, 21, 34, 55, 89, 144..."

```{r}


```

Write a recursive function that sorts a randomly generated list of decimal vector values:

```{r}

list <- runif(100)



```

Finding sum of series 1²+2²+3²+…..+n² using a recursive function

```{r}


```

