---
title: "For Loops in R"
author: "Audrey Olson"
date: "5/25/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

These are taken directly from https://www.r-exercises.com/2018/03/30/loops-in-r-exercises/

Exercise 1

Write a for loop that iterates over the numbers 1 to 7 and prints the cube of each number using print().

```{r}

for (i in 1:7) {
  print(i^3)
}

```


Exercise 2

Write a for loop that iterates over the column names of the inbuilt iris dataset and print each together with the number of characters in the column name in parenthesis. Example output: Sepal.Length (12). Use the following functions print(), paste0() and nchar().

```{r}

iris

for (n in names(iris)) {
  print(paste0(n, " (", nchar(n), ")"))
}


```


Exercise 3

Write a while loop that prints out standard random normal numbers (use rnorm()) but stops (breaks) if you get a number bigger than 1.

```{r}

set.seed(3)

while (TRUE) {
  x <- rnorm(1)
  print(x)
  if (x > 1) {
    break
  }
}

```


Exercise 4

Using next adapt the loop from last exercise so that doesn’t print negative numbers.

```{r}

set.seed(3)

while (TRUE) {
  x <- rnorm(1)
  if (x < 0) {
    next
  }
  print(x)
  if (x > 1) {
    break
  }
}

```


Exercise 5

Using a for loop simulate the flip a coin twenty times, keeping track of the individual outcomes (1 = heads, 0 = tails) in a vector that you preallocte.

```{r}

n <- 20
coin_outc <- vector(length = n, mode = "integer")
for (i in 1:20) {
  coin_outc[i] <- sample(c(0L, 1L), 1)
}
coin_outc

```


Exercise 6

Use a nested for loop (a for loop inside a for loop) that produces the following matrix, preallocate the matrix with NA values.

    0     1     2     3     4
    1     0     1     2     3
    2     1     0     1     2
    3     2     1     0     1
    4     3     2     1     0
    
```{r}

mat <- matrix(NA_integer_, nrow = 5, ncol = 5)
for (i in 1:5) {
  for (j in 1:5) {
    mat[i, j] <- abs(i - j)
  }
} 

mat

```


Exercise 7

Use a while loop to investigate the number of terms required before the product

1⋅2⋅3⋅4⋅…

reaches above 10 million.

```{r}

target <- 1e8
product <- 1
n <- 0
while (product <= target) {
  n <- n + 1
  product <- product*n
}

n

```


Exercise 8

Use a while loop to simulate one stock price path starting at 100 and random normally distributed percentage jumps with mean 0 and standard deviation of 0.01 each period. How long does it take to reach above 150 or below 50?

```{r}

set.seed(22)

price_start <- 100
price <- price_start
target_diff <- 50
n <- 0
while (abs(price_start - price) < target_diff) {
  n <- n + 1
  price <- price*(1 + rnorm(mean = 0, sd = 0.01, n = 1))
}

n

```


Exercise 9

Implement a simple version of Guess the number game using a while loop. The user should guess a number between 1 and 10, you can use scan() to get user input. The loop should break if the user guesses 5.

```{r}

# NOTE: THESE FINAL TWO SOLUTIONS WILL NOT RUN AS INTENDED IN RMD. YOU WILL NEED TO RUN THESE SCRIPTS IN A REGULAR R SCRIPT FILE THROUGH THE CONSOLE, TO SEE THEM WORKING. THIS IS BECAUSE OF HOW THE WHILE LOOPS READ IN THE INPUT.

x <- 0L
while (TRUE) {
  cat(
    "I am thinking of a number between 1 and 10.",
    "\nTake a guess and press enter twice!"
  )
  x <- scan("")
  if (x == 5L) {
    cat("Right!")
    break
  }
  cat("Wrong\n")
}

```


Exercise 10

Implement a multiplication game. A while loop that gives the user two random numbers from 2 to 12 and asks the user to multiply them. Only exit the loop after five correct answers. Try using as.integer(readline()) instead of scan() this time.

```{r}

total <- 0
while (TRUE) {
  if (!total %in% 0:4) {
    total <- 0L
  }
  n <- sample(c(2:12), 2)
  cat("What is the product of ", n[1], " and ", n[2], "?\n", sep = "")
  x <- as.integer(readline())
  if (x == prod(n)) {
    total <- total + 1L
    cat("Right!")
    if (total == 5) break
    cat(" You just need", 5 - total, "more answers.\n\n")
  } else {
    cat("Wrong\n")
  }
}

```

